Maximizing Ink in Symmetric Partial Edge Drawings of $k$-plane Graphs

### 2018-01-09 eurocg/paper.tex
4.1 done

\begin{figure}[tbp]
	\centering
 	\includegraphics{tree_illustration}
	\caption{A segment with  intersecting segments and the different induced stub lengths.} % The shaded areas are the stubs, $ p(u) $ is the parent of $ u $. The stubs in the boxed area contribute to $ \solshort(u) $.}
	\label{fig:tree}
\end{figure}

@@

@@

\section{Conclusion}

\bibliography{paper}

\end{document}

>>>>

\begin{figure}[tbp]
	\centering
 	\includegraphics{tree_illustration}
	\caption{A segment $s(u)$ with five intersecting segments and the different induced stub lengths. The boxed stub lengths are considered in $\solshort(u)$.} % The shaded areas are the stubs, $ p(u) $ is the parent of $ u $. The stubs in the boxed area contribute to $ \solshort(u) $.}
	\label{fig:tree}
\end{figure}

@@

% \begin{figure}[tbp]
% 	\centering
%  	\includegraphics{tree_illustration}
% 	\caption{One edge $ s(u) $ with intersecting segments. The shaded areas are the stubs, $ p(u) $ is the parent of $ u $. The stubs in the boxed area contribute to $ \solshort(u) $.}
% 	\label{fig:tree}
% \end{figure}

@@

\bibliography{paper}
\end{document}
